Food-web complexity flattens the fitness landscape of an insect herbivore

### 2018-07-04 elsevier_test/elsevier_test.tex
broke chunks into sizes less than 100 MB. enhanced plot aesthetics.

\begin{verbatim}
##           Phenotype Food_Web Model Type Estimate lower_2.5 upper_97.5
## 1     Gall diameter  Complex  GLMM Beta    0.555     0.426      0.683
## 2       Clutch size  Complex  GLMM Beta    0.036    -0.090      0.169
## 3 Female preference  Complex  GLMM Beta    0.003    -0.185      0.131
## 4         Gall size   Simple  GLMM Beta    0.289     0.208      0.339
## 5       Clutch size   Simple  GLMM Beta   -0.102    -0.190     -0.010
## 6 Female preference   Simple  GLMM Beta   -0.204    -0.291     -0.097
\end{verbatim}

\begin{verbatim}
##           Phenotype Food_Web Model      Type Estimate lower_2.5 upper_97.5
## 1     Gall diameter  Complex  GLMM Quadratic    0.050    -0.084      0.164
## 2       Clutch size  Complex  GLMM Quadratic    0.000    -0.232      0.260
## 3 Female preference  Complex  GLMM Quadratic    0.032    -0.098      0.154
## 4         Gall size   Simple  GLMM Quadratic    0.090    -0.104      0.236
## 5       Clutch size   Simple  GLMM Quadratic    0.032    -0.070      0.170
## 6 Female preference   Simple  GLMM Quadratic    0.204     0.078      0.408
\end{verbatim}

\begin{verbatim}
##     Phenotype Food_Web Model          Type Estimate lower_2.5 upper_97.5
## 1 Diam,Clutch  Complex  GLMM Correlational   -0.028    -0.145      0.055
## 2   Diam,Pref  Complex  GLMM Correlational   -0.104    -0.302      0.165
## 3 Clutch,Pref  Complex  GLMM Correlational    0.004    -0.079      0.120
## 4 Diam,Clutch   Simple  GLMM Correlational   -0.106    -0.161      0.048
## 5   Diam,Pref   Simple  GLMM Correlational    0.003    -0.052      0.093
## 6 Clutch,Pref   Simple  GLMM Correlational   -0.021    -0.167      0.085
\end{verbatim}

@@

BREAK UP INTO INDIVIDUAL PIECES: E.G. GALL SIZE. THIS SHOULD BE SMALL
ENOUGH TO ALLOW CACHING

\includegraphics{elsevier_test_files/figure-latex/Plot Univariate Landscapes-1.pdf}

\includegraphics{elsevier_test_files/figure-latex/Plot Multivariate Fitness Landscape-1.pdf}

@@

\includegraphics{elsevier_test_files/figure-latex/Univariate Absolute Fitness Landscapes-1.pdf}

\includegraphics{elsevier_test_files/figure-latex/Multivariate Absolute Fitness Landscapes-1.pdf}

>>>>

\begin{verbatim}
##           Phenotype Food_Web Model Type Estimate lower_2.5 upper_97.5
## 1     Gall diameter  Complex  GLMM Beta    0.555     0.432      0.642
## 2       Clutch size  Complex  GLMM Beta    0.036    -0.075      0.177
## 3 Female preference  Complex  GLMM Beta    0.003    -0.228      0.148
## 4         Gall size   Simple  GLMM Beta    0.289     0.220      0.357
## 5       Clutch size   Simple  GLMM Beta   -0.102    -0.190     -0.001
## 6 Female preference   Simple  GLMM Beta   -0.204    -0.273     -0.119
\end{verbatim}

\begin{verbatim}
##           Phenotype Food_Web Model      Type Estimate lower_2.5 upper_97.5
## 1     Gall diameter  Complex  GLMM Quadratic    0.050    -0.052      0.218
## 2       Clutch size  Complex  GLMM Quadratic    0.000    -0.186      0.254
## 3 Female preference  Complex  GLMM Quadratic    0.032    -0.078      0.146
## 4         Gall size   Simple  GLMM Quadratic    0.090    -0.078      0.266
## 5       Clutch size   Simple  GLMM Quadratic    0.032    -0.070      0.156
## 6 Female preference   Simple  GLMM Quadratic    0.204    -0.008      0.446
\end{verbatim}

\begin{verbatim}
##     Phenotype Food_Web Model          Type Estimate lower_2.5 upper_97.5
## 1 Diam,Clutch  Complex  GLMM Correlational   -0.028    -0.085      0.076
## 2   Diam,Pref  Complex  GLMM Correlational   -0.104    -0.274      0.074
## 3 Clutch,Pref  Complex  GLMM Correlational    0.004    -0.109      0.063
## 4 Diam,Clutch   Simple  GLMM Correlational   -0.106    -0.215      0.029
## 5   Diam,Pref   Simple  GLMM Correlational    0.003    -0.064      0.097
## 6 Clutch,Pref   Simple  GLMM Correlational   -0.021    -0.156      0.045
\end{verbatim}

\begin{figure}[htbp]
\centering
\includegraphics{complex_simple_foodwebs_compressed.pdf}
\caption{Illustrations of complex (A) and simple (B) food webs
associated with the insect herbivore, \emph{Iteomyia salicisverruca}.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{elsevier_test_files/figure-latex/Figure 2 Univariate Landscapes-1.pdf}
\caption{Selection gradients acting on gall traits in complex vs.~simple
food webs. Each panel corresponds to a different gall trait: gall
diameter (A); clutch size (B); and female preference (C). Solid lines
represent the estimated gradients in complex (orange) and simple (blue)
food webs. Transparent lines represent bootstrapped replicates (n=100)
to show the uncertainty in estimated gradients.}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\begin{figure}[htbp]
\centering
\includegraphics{elsevier_test_files/figure-latex/Figure 3 Multivariate Landscapes-1.pdf}
\caption{Relative fitness landscapes of gall traits in complex
vs.~simple food webs. Each panel corresponds to a different combination
of traits: clutch size and gall diameter (A); clutch size and female
preference (B); female preference and gall diameter (C). Note that
traits for all plots range 1 SD below and above the mean (=0).}
\end{figure}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

@@

\includegraphics{elsevier_test_files/figure-latex/Figure S1 Univariate Absolute Fitness Landscapes-1.pdf}

\includegraphics{elsevier_test_files/figure-latex/Figure S2 Multivariate Absolute Fitness Landscapes-1.pdf}
